|

### 2020-11-26 01-Chp1-Introduction.Rmd
Small starter fixes
Clean-up for today - ahead!

```{r}
f <- flextable::flextable(robvis::data_rob2)

f <- flextable::autofit(f)

f
```

@@

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`. The motivation for, development and impact of, and future plans for these tools are outlined.
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes the
* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regaulting agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref():__ This Chapter seeks

@@

* Talk at Cochrane on medrxivr
* Webinar to Evidence Synthesis Ireland on Risk of Bias test

>>>>

@@

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between  
* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref():__ This Chapter seeks

* __Appendix \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`. The motivation for, development and impact of, and future plans for these tools are outlined.

@@

* Talk at Cochrane on medrxivr
* Presentation to the 
* Webinar to Evidence Synthesis Ireland on Risk of Bias

### 2020-11-26 03-Chp2-Systematic-Review.Rmd
Clean-up for today - ahead!

@@

Those records which were excluded in the inital screening , but were included either by the same reviewer on their second vieweing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.

@@

```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review."}
```

Following deduplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened.

@@

XXXX studies met the criteria for inclusion in the review

####

@@

>>>>

Data will be visualized using a paired forest and risk of bias plot

@@

Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.

@@

```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review.", out.width="100%"}
```

Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened. [**CROSS-REF to PRISMA flow here**]

@@

XXXX studies met the criteria for inclusion in the review.

Include here:

* PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)

* Summary of types of study

* Summary of locations

* Summary of diagnostic criteria used

* Summary of risk of bias

* Long table, horizontally. Newer version of flextable (GH) allows for PDF output

## Publication bias

* Check if there are protocols available for any of the published reports, and whether there were
* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

### Triangualtion across evidence sources

One key question for which multiple distinct sources of evidence were available were those looking at Laz

A key limitiation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use

@@

Of note, as part of the review, we identified serveral previous systematic reviews of this topic. However, this review is the firest to

### 2020-11-26 04-Ch3-CPRD-Analysis.Rmd
Clean-up for today - ahead!

Might be able to get around this by pointing

@@

@@

It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the liklihood of someone being prescribed a statin.

>>>>

Might be able to get around this by pointing out

## Things we tried

- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than. Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly. Need total number of those starting and average time to start.
- Positive controls. Need to be able to explain why these controls have such wildly increased results.
- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
- Allowing for time-varying confounders for binary covariates.
- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.

## Things we could try

- Work through data using positive control to see if the way it is being added is what is causing the issues.
- Examine Cramer et al. thesis and see what they did
- Marginal structural models approach (a la J. Sterne)

@@

In this

@@

It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.

### 2020-11-26 05-Chp-Systematic-Review-Tools.Rmd
Clean-up for today - ahead!

``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", out.height = "100%", fig.align = "centre"}

@@

tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15)

ggplot2::ggsave(
          filename = "figures/sys-rev-tools/example-rob-traffic-light-plot.png",
          plot = tfplot,
          width = 7,
          height = 8,
          dpi = 400
          )

knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png")
```

@@

``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%", out.height = "100%"}

sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black"),
                  axis.text.y = ggplot2::element_text(size = 6)
                  )

ggplot2::ggsave(
          filename = "figures/sys-rev-tools/example-rob-summary-barplot.png",
          plot = sumplot,
          width = 8,
          height = 2.41,
          dpi = 400
          )

>>>>

``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}

@@

tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)

robvis::rob_save(tfplot, 
                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")

knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
```

@@

``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}

sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)

robvis::rob_save(sumplot,
                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")

### 2020-11-26 front-and-back-matter/_00-introduction.Rmd
Clean-up for today - ahead!

files <- list.files(pattern = "\\.Rmd$")

files <- files[which(files != "index.Rmd")]

@@

for (file in 1:length(files)) {
  tmp <- wordcountaddin::word_count(files[file])
  words_v <- c(words_v, tmp)
}

@@

@@

words_behind <- target - words$words[which(words$date == max(words$date))]

@@

Word count: `r words$words`

@@

>>>>

files <- list.files(path = here::here(), pattern = "\\.Rmd$")

files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]

@@

for (file in 1:length(files)) {
  tmp <- wordcountaddin::word_count(here::here(files[file]))
  words_v <- c(words_v, tmp)
}

@@

words_today <- words$words[which(as.Date(words$date, format="%Y%m%d")==max_date)]

@@

words_behind <- words$words[which(words$date == max(words$date))] - target

@@

Word count: `r words_today`

@@

&nbsp;

&nbsp;

### 2020-11-26 index.Rmd
Clean-up for today - ahead!

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

>>>>

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?
